Python as a machine learning language: experiences from the \sklearn project

### 2013-06-11 paper.tex
remove subsection about method chaining (too detailed)

The API is designed to adhere to the following broad principles:
\begin{description}
  \item[Inspectability.]
       \sklearn objects store their constructor parameters
       as well as parameter values determined by learning algorithms
       as public attributes in a documented format.
       (The Python language does not actually distinguish
       between public and private attributes of objects,
       but by convention, any identifier
       prefixed with an underscore (\texttt{\_})
       is considered ``a non-public part of the API''; \citealp{pythontut}.)
  \item[No proliferation of classes.]
       Learning algorithms are objects of custom classes,
       but datasets and hyperparameter names and values,
       are represented as standard Python, NumPy and SciPy classes
       rather than custom ones whenever feasible.
       Custom classes adhere to Python conventions and protocols
       for constructs such as iteration over the ``folds''
       in a $k$-fold cross validation.
       This should keep \sklearn easy to use
       and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  \item[Composability.]
       Many machine learning tasks are expressible
       as \textit{pipelines} of transformations to data.
       Other tasks are naturally viewed
       as modifications to other tasks;
       e.g., multi-label classification
       can be reduced to multiple binary classification tasks.
       Accordingly, multi-label classification
       is implemented by a class that takes an existing classifier object
       as input and modifies its function.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default value for that parameter must be defined by the library
       if at all possible,
       and the default should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

@@

\subsection{Method chaining}

In \sklearn, the \texttt{fit} method always returns the estimator
it was called on, hence making method chaining possible.  Using this technique,
we can thus rewrite the \texttt{StandardScaler} example above in a single line:
\begin{verbatim} 
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{verbatim} 
In addition, \texttt{fit(X\_train).transform(X\_train)} can further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single method \texttt{fit\_transform}
allows to share computations, which often makes a huge difference in practice.
In the same spirit, \sklearn sometimes provides the
\texttt{fit\_predict} method for combining the \texttt{fit} and \texttt{predict}
methods. This is especially useful for retrieving cluster predictions with
respect to the training data \texttt{X\_train} in clustering algorithms.

@@

% Construction and application of an estimator object
% proceeds in a way that is somewhat reminiscent of partial function application.
% The constructor, \texttt{\_\_init\_\_}\footnote{
%   Strictly speaking, \texttt{\_\_init\_\_} is Python's
%   class \textit{initialization} method,
%   while \texttt{\_\_new\_\_} is the constructor.
%   The distinction is not relevant to the present description of scikit-learn.}
% takes a set of named (hyper-)parameters
% and attaches these to the estimator as public attributes.
% It never performs actual learning, nor does it even see a training set.

>>>>

@@

@@

% Construction and application of an estimator object
% proceeds in a way that is somewhat reminiscent of partial function application.
% The constructor, \texttt{\_\_init\_\_}\footnote{
%   Strictly speaking, \texttt{\_\_init\_\_} is Python's
%   class \textit{initialization} method,
%   while \texttt{\_\_new\_\_} is the constructor.
%   The distinction is not relevant to the present description of scikit-learn.}
% takes a set of named (hyper-)parameters
% and attaches these to the estimator as public attributes.\footnote{
%   The Python language does not actually distinguish between public and private
%   attributes and methods,
%   but by convention, any identifier prefixed with an underscore (\texttt{\_})
%   is considered ``a non-public part of the API\ldots
%   an implementation detail and subject to change without notice.''
%   \Citep{pythontut}
%   }
% It never performs actual learning, nor does it even see a training set.
